Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
reformat tab:corpus

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{subfigure}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{group-separator={,},group-minimum-digits={3},output-decimal-marker={.}}
\usepackage{tikz}
\usepackage{xypic}

@@

Thus far we have explained the model of regions as sets of index
schemes, that is
$\interp{\textit{region}}_n \in \mathcal{P}(\domainVal{}^n)$.
Figure~\ref{fig:spatial-model} defines the top-level model of the
\textit{spec} syntax, which includes the multiplicity and
approximation modifiers.

@@

\subsection{Software Corpus}
\begin{table}
\centering
\sisetup{
  table-format = 7,
  table-number-alignment = right
}
\begin{tabular}{|l|S|S|S|}
\hline
Package   & {Files} & {Files analysed} & {Lines of code}  \\ % braces prevent headers from being formatted as numbers
\hline
UM        & \umFiles                       & \umparseOk                      & \umLoC                     \\
E3MG      & \ethreemgeaFiles               & \ethreemgeaparseOk              & \ethreemgeaLoC             \\
BLAS      & \blasFiles                     & \blasparseOk                    & \blasLoC                   \\
Hybrid4   & \hybridfourFiles               & \hybridfourparseOk              & \hybridfourLoC             \\
GEOS-Chem & \geoschemFiles                 & \geoschemparseOk                & \geoschemLoC               \\
Navier    & \navierFiles                   & \navierparseOk                  & \navierLoC                 \\
CP        & \computationalphysicstwoFiles  & \computationalphysicstwoparseOk & \computationalphysicstwoLoC\\
\hline
\textbf{Total} & \overallFiles  & \overallparseOk & \overallLoC  \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{tab:corpus}}
\end{table}

Table~\ref{tab:corpus} shows summary statistics of the software
packages used in our evaluation, all of which are written in Fortran
90 or Fortran 77. In total we analysed 1.1 million lines of code from
7 packages. The ``Files analysed'' column shows the number of files in
each corpus that we were able to analyse with Camfort. The most common
reasons for Camfort rejecting a file were either use of a
C-preprocessor, or illegal use of language features from a more modern
Fortran variant.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{subfigure}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

\usepackage{tikz}
\usepackage{xypic}

@@

We have explained the model of regions as sets of index
schemes, that is
$\interp{\textit{region}}_n \in \mathcal{P}(\domainVal{}^n)$.
Figure~\ref{fig:spatial-model} defines the top-level model of the
\textit{spec} syntax, which includes the multiplicity and
approximation modifiers. The domain of this interepretation
is $\textsf{Mult}(\textsf{Approx}(\mathcal{P}(\domainVal{}^n)))$
where $\textsf{Mult}$ and $\textsf{Approx}$ are labelled variants
labelling our set-basd model with additional information.

\begin{definition} The \textsf{Mult}
and \textsf{Approx} are parametric labelled variant (sum) types 
with injection function given by their definition:
%
\begin{align*}
\textsf{Mult} \, a & = \textsf{mult} \, a \,\mid\, \textsf{only} \, a \\
\textsf{Approx} \, a & = \textsf{exact} \, a \,\mid\, \textsf{lower} \, a \,\mid\,
\textsf{upper} \, a \,\mid\, \textsf{both} \, a \, a
\end{align*}
\ie{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \rightarrow \mathsf{Approx} \, a$, and so
on. These are used for labelled models, and other components later in
Section~\ref{sec:analysis} with additional information.
\label{def:mult-and-approx}
\end{definition}
%

@@

\subsection{Software Corpus}
\begin{table}
\centering
\footnotesize
\begin{tabular}{lSSSS}
\hline
& \multicolumn{2}{c}{Number of files} & \multicolumn{2}{c}{Lines of code} \\

Package   & {Total} & {Parsed} & {Total} & {Parsed}  \\ % braces prevent headers from being formatted as numbers
\hline
UM        & \umFiles                       & \umparseOk                      & \umLoC                      & \umlinesParsed \\
E3MG      & \ethreemgeaFiles               & \ethreemgeaparseOk              & \ethreemgeaLoC              & \ethreemgealinesParsed \\
BLAS      & \blasFiles                     & \blasparseOk                    & \blasLoC                    & \blaslinesParsed \\
Hybrid4   & \hybridfourFiles               & \hybridfourparseOk              & \hybridfourLoC              & \hybridfourlinesParsed \\
GEOS-Chem & \geoschemFiles                 & \geoschemparseOk                & \geoschemLoC                & \geoschemlinesParsed \\
Navier    & \navierFiles                   & \navierparseOk                  & \navierLoC                  & \navierlinesParsed \\
CP        & \computationalphysicstwoFiles  & \computationalphysicstwoparseOk & \computationalphysicstwoLoC & \computationalphysicstwolinesParsed \\
\hline
\textbf{Total} & \overallFiles  & \overallparseOk & \overallLoC & \overalllinesParsed \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{tab:corpus}}
\end{table}

Table~\ref{tab:corpus} shows summary statistics of the software
packages used in our evaluation, all of which are written in Fortran
90 or Fortran 77. In total we analysed \SI{\overallLoC} lines of code
from 7 packages, of which we successfully parsed
\SI{\overalllinesParsed} lines. The ``Number of files'' column shows
how many files in each corpus that we were able to analyse with
Camfort. The most common reasons for Camfort rejecting a file were
either use of a C-preprocessor, or illegal use of language features
from a more modern Fortran variant.
